Index measures for oak decline severity using phenotypic descriptors

### 2019-11-12 manuscript/manuscript.Rmd
phenotypic descriptor info table added to plan
fixed descriptor table, site difference rf plot and DI space plot
manuscript now compiles
fixed DAI inversion

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      cache = TRUE,
                      fig.pos = 'H',
                      warning = FALSE,
                      message = FALSE)
```

```{r library_load,cache=FALSE}
source('../code/library_load.R')
```

```{r prep}
source('../code/data_prep.R')
```

@@

## Figures

```{r figures,child='figures.Rmd'}

```

```{r check,comment='',cache=FALSE}
source('../code/check.R')
manuscript_check()
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      #cache = TRUE,
                      fig.pos = 'H',
                      warning = FALSE,
                      message = FALSE)
```

@@

```{r check,comment='',cache=FALSE}
manuscript_check()
```
